### 2016-02-23 experiments.tex
more edits

These data sets, though similar in that both compilers are written in C, provide some interesting variance for testing our hypotheses.  The oracle for SpiderMonkey executions is the set of checks built in to {\tt jsfunfuzz} plus the requirement that the execution not crash.   If the {\tt jsfunfuzz} produced test case executes to the end and prints {\tt TEST SUCCESSFULLY COMPLETED} it is considered successful.  This is only a moderately strong oracle, and allows serious deviations in behavior from both the JavaScript language specification and normal SpiderMonkey behavior, while constraining other some of execution fairly tightly, such as {\tt eval} round-trips.  For GCC, the oracle is a differential check on a hash code:  failure was defined as producing a executable with the -O3 flag that, when executed, produced a different checksum than code compiled by either of GCC 4.9.3 or clang 7.0.0, both using -O0.  A repairing mutant must enable GCC 4.3.0 to actually compile code correctly, which is a very strict correctness property, making coincidental correctness \cite{CCT} highly unlikely.  The only weakness is that there is no check on speed of or time to produce compiled code.

>>>>

These data sets, though similar in that both compilers are written in C, provide some interesting variance for testing our hypotheses.  The oracle for SpiderMonkey executions is the set of checks built in to {\tt jsfunfuzz} plus the requirement that the execution not crash.   If the {\tt jsfunfuzz} produced test case executes to the end and prints {\tt TEST SUCCESSFULLY COMPLETED} it is considered successful.  This is only a moderately strong oracle, and allows serious deviations in behavior from both the JavaScript language specification and normal SpiderMonkey behavior, while constraining other aspects of execution fairly tightly, such as {\tt eval} round-trips.  For GCC, the oracle is a differential check on a hash code:  failure was defined as producing a executable with the -O3 flag that, when executed, produced a different checksum than code compiled by either of GCC 4.9.3 or clang 7.0.0, both using -O0.  A repairing mutant must enable GCC 4.3.0 to actually compile code correctly, which is a very strict correctness property, making coincidental correctness \cite{CCT} highly unlikely.  The only weakness is that there is no check on speed of or time to produce compiled code.
